### 2025-07-18 paper-reviews/papers-2025.tex
Add approximate computing paper

    The paper presents AVX512-based base64 encoding and decoding implementation. The implementation achieves five and seven-fold improvement compared to AVX2-based implementation for decoding and encoding correspondingly. The implementation uses AVX512 BMI instructions in a nice way that allows to decode/encode base64 at speed close to memory copy.
\end{itemize}

>>>>

    The paper presents AVX512-based base64 encoding and decoding implementation. The implementation achieves five and seven-fold improvement compared to AVX2-based implementation for decoding and encoding correspondingly. The implementation uses AVX512 BMI instructions in a nice way that allows to decode/encode base64 at speed close to memory copy.

    \item \cite{Agrawal:ApproximateComputing:2016}:

    The paper explores approximate computing techniques applied to a set applications that do not require exact calculations. The techniques explored in the paper include: loop perforation (omitting executing of some loop iterations), reduced precision for floating point calculations and relaxed synchronization for concurrent execution. The authors show that the techniques can be combined together in many cases. How and what techniques are to be used depend on the application. The resulting performance improvements also varies with the application.
\end{itemize}
